Discovery of Mg-depleted and K-enhanced Stars in \textit{LAMOST}

### 2018-02-05 article/msarchive5feb2018.tex
draft prior proofreading tmo. also archive of what it was before draft

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Kemp et al.]{Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
Andrew R. Casey,$^{1,2}$
Matthew T. Miles,$^{1}$
Brodie J. Norfolk,$^{1}$\newauthor
John C. Lattanzio,$^{1}$
Amanda I. Karakas,$^{1}$
Kevin C. Schlaufman,$^{3}$
Anna Y.~Q. Ho,$^{4}$\newauthor
Christopher A. Tout$^{1,5}$
%Melissa K. Ness,$^{5}$
%David W. Hogg,$^{6}$
\\
% List of institutions
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{5}$Institute of Astronomy, Madingley Road, Cambridge CH30HA, United Kingdom
%$^{5}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
%$^{6}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
}

% These dates will be filled out by the publisher
\date{Accepted 2018 XX XX. Received 2018 YY YY; in original form 2018 ZZ ZZ}

@@

\begin{abstract}
Stars with unusual elemental abundances offer clues about rare astrophysical events or nucleosynthetic pathways. Stars with significantly depleted magnesium and enhanced potassium (e.g., $[{\rm K}/{\rm Fe}] > 1$; $[{\rm Mg}/{\rm Fe}] < -0.5$) have to date only been found in the massive globular cluster NGC~2419, and to a lesser extent, NGC~2808. The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and depleted [Mg/Fe] abundance ratios.
Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
\todo{We conclude what about the origin. What does this imply.}
This sample will help guide modelling attempts to explain the origin for the Mg-K abundance signature, which we show exists throughout the Milky Way.
\end{abstract}

@@

An early modelling attempt at replicating the anomalous Mg/K abundance ratios assumed hot-bottom burning in AGB and super-AGB (SAGB) stars. \cite{ventura2012} succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K. However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value. or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.

A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}. The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway. The main pathway \cite{iliadis2016} identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary. This constraint rules out many pollution sites, including: core and shell burning of low-mass stars, high-mass and super-massive stars, as well as regular AGB stars. Super-AGB (SAGB) stars, however, were considered as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified. The other potential candidate identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty. However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.

@@

One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae. However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419. In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude \todo{[citations]}. Another mechanism for reducing [Mg/Fe] is through the Mg-Al nucleosynthetic chain in high temperature hydrogen burning. However, no Al correlation is observed with the Mg depletions in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.

@@

We identified potential Mg-depleted and K-enhanced stars by searching for significant deviations in residual flux. The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$). A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model). Figure \ref{fig:posterchild} shows the \lamost\ spectra, and best-fitting model from \tc, for candidate J034458.82+592955.1.

@@

We estimated [K/Fe] abundance ratios for all candidates by synthesising spectra to account for the flux residuals \citep{marcs,sme,vald,ispec}. We assume that absorption due to metals is accounted for by \tc, and deviations in flux around the potassium doublet is due to an increased [K/Fe] with respect to the model. We list estimated [K/Fe] abundance ratios in Table 1, where the error includes a 0.2\,dex systematic error floor that we have applied in quadrature with the fitting errors. We applied the same method to estimate [Na/Fe] from \lamost\ spectra. We note that while enhancements in [K/Fe] or [Na/Fe] can be estimated by synthesising the flux residuals, we cannot easily estimate [Mg/Fe] depletions in the same manner because it is difficult to separate the flux contribution of [Mg/Fe] (from [$\alpha$/Fe]) from the data-driven model. For this reason, we will adopt [$\alpha$/Fe] as a conservative upper limit for [Mg/Fe].

%\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra. Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5 dex. \todo{@andy add anything specific to Na abundance methods from LAMOST}.

@@

\subsection{Detailed chemical abundances}
\label{sec:abundances}
Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. As described in Section \ref{sec:method}, we adopt [$\alpha$/Fe] as an upper limit for [Mg/Fe]. [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown. \todo{For these stars..}

%The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1 dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data. However, for the bulk of the sample decoupling [Mg/Fe] from $[\alpha$/Fe] is impossible, and so in general  we are unable to draw firm conclusions as to whether the sample exhibits anomalously low [Mg/Fe].

[K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population. \todo{It is noteworthy that both of these populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars. --> What?}
Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe] the exact level of Mg depletion for the candidates is unclear. The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419, although the small sample of these stars for which we have high resolution spectra means we are unable to confidently generalise this to the entire sample.

A similar relationship emerges when these abundances with typical galactic abundances for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3. Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample has extremely high levels of [K/Fe].

The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, \todo{which is absent from measurements in the Milky Way}. This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases. It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation. \todo{make figure in python, add trend line}

@@

The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], as were the levels of [Mg/Fe] from the high resolution Magellan/MIKE spectra. Once again the inability to decouple [Mg/Fe] from $[\alpha$/Fe] means we are unable do draw firm conclusions about whether [Mg/Fe] is depleted relative to typical field stars, although the data we do have suggests not. No variation with metallicity is observed for [$\alpha$/Fe], including GCE effects relating of Type Ia supernovae enrichments.

%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3 dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}. No variation with metallicity is observed within the \lamost sample's [$\alpha$/Fe].

[Na/Fe] was also measured for the \lamost\ data. Two distinct populations were observed, with a substantial minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}. However, this behaviour is very likely due to the effect of interstellar dust. This conclusion is based on values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, which were notably higher for the stars supposedly enriched in Na than for those consistent with galactic levels. \todo{It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K. For these newly identified candidate stars, no relation between Na and K abundance is observed.}

The implications of the calculated abundances are intriguing. The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness regarding the extreme bi-modal nature of its abundance pattern. It is worth repeating however that the sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.

The 112 star candidate pool of K enhanced stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels at a range of metallicities. It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.

\subsection{Impact scenarios regarding the Mg-K anti-correlation}

@@

The spread in metallicities among our candidates is important to note. This implies that the process responsible for the Mg-K abundance signature is not necessarily tied to a certain epoch in the Milky Way's evolution. Rather, stars with enhanced K and depleted magnesium tend to form at all ages, across all metallicities. A hyper-massive Population III star may have been a plausible explanation for NGC~2419\todo{[CITATIONS NEEDED: WHO PROPOSED THIS]}, particularly given it's isolation from the Milky Way ($d_{GC} \approx 90\,{\rm kpc}$) and low metallicity. However, our discovery of Mg-K stars at all metallicities suggests against a hyper-massive Population III star as the polluter responsible.

As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K. Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27} Al} through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}. This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system.

Allowing different sites for Mg depletion and K enrichment, one scenario that could possibly produce a large K enhanced signature -- along with (inconsistently) depleted Mg and enhanced Na -- throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is a less massive star. The scenario might proceed as follows:

The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope. It then deposits its K rich outer layers onto its smaller companion through wind-based accretion. This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not. If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced \citep{prantzos2017}, with this material mixed throughout the envelope. In this scenario, it is observations of this smaller binary companion star that make up our sample of 112 giants.

Although this scenario allows for consistency with the total spread in metallicity, it doe not account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation. \todo{The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.}

A direct test of this scenario would be whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.

The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases. This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419. If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 112 field star sample.

Suppose some unknown event(s) unique to very metal poor (possibly zero-metallicity) environments occurs. This event results in a gas cloud depleted in Mg and enhanced in K. The generation of stars that form directly from this gas carries this signature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419's extreme population. We will refer to this generation of stars Generation 1.

When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which is very difficult to form in significant quantities. The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg released by Generation 1. The K enhancement however remains (in principle) relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released. As this cycle continues, [K/Fe] would continue to lower proportionately with the rate of iron release, while depletions in [Mg/Fe] would quickly become impossible to detect.

This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form at most 2 generations of stars. But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form. Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419. Certainly the idea that both groups of anomalous stars arise from the same polluter source must be entertained.

\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg-depleted, K enriched material in the first place must be emphasized. Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible. If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe]. But as soon significant amounts of iron are added, [Fe/H] for the subsequent Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}. This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).}

Another issue facing the above scenario is that it requires a single gas cloud to form many generations of stars to be formed almost continously to be consistent with Figure \ref{KvsFe}. This is only known to occur in inside galaxies, which are massive enough and have sufficient gas to form multiple star forming regions. For smaller gas clouds, typically only one generation is formed before the remaining gas is lost through stellar winds. Although it is tempting to attempt to satisfy such concerns by allowing the stars to have formed some dwarf galaxy which then merged with the Milky Way, if the initial gas cloud increases so significantly in mass, then the difficulty of polluting such a cloud in the first place with such high levels of K increases proportionately.

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Kemp et al.]{
Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
Andrew R. Casey,$^{1,2}$
Mathew T. Miles,$^{1}$
Brodie J. Norfolk,$^{1}$\newauthor
John C. Lattanzio,$^{1}$
Amanda I. Karakas,$^{1}$
Kevin C. Schlaufman,$^{4}$\newauthor
Christopher A. Tout, $^{3}$
Anna Y.Q Ho,$^{5}$
Melissa K. Ness,$^{6}$
David W. Hogg, $^{7}$
\\
% List of institutions
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$ Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$ Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom
$^{4}$, Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
$^{5}$ Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{6}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
$^{7}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
}
% These dates will be filled out by the publisher
\date{Accepted 2018 XX XX. Received 2018 YY YY; in original form 2018 ZZ ZZ}

@@

\begin{abstract}
Stars with unusual elemental abundances offer clues about rare astrophysical events or nucleosynthetic pathways. Stars with significantly depleted magnesium and enhanced potassium (e.g., $[{\rm K}/{\rm Fe}] > 1$; $[{\rm Mg}/{\rm Fe}] < -0.5$) have to date only been found in the massive globular cluster NGC~2419, and to a lesser extent, NGC~2808. The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and possibly depleted [Mg/Fe] abundance ratios.
Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
We conclude that nucleosynthetic process producing the anomalous abundances in [K/Fe] and [Mg/Fe] is probably (but not necessarily) present at a wide range of metallicities. This makes polluter candidates which are limited to a certain epoch in GCE unlikely solutions.
This sample will help guide modelling attempts to explain the origin for the Mg-K abundance signature, which we show exists throughout the Milky Way.
\end{abstract}

@@

@@

One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae. However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419. In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude \citep{ventura2012,iliadis2016}. Another mechanism for reducing [Mg/Fe] is through the Mg-Al nucleosynthetic chain in high temperature hydrogen burning. However, no Al correlation is observed with the Mg depletions in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.

@@

We identified potential Mg-depleted and K-enhanced stars by searching for significant deviations in residual flux. The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$). A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model). Figure \ref{posterchild} shows the \lamost\ spectra, and best-fitting model from \tc, for candidate J034458.82+592955.1.

@@

We estimated [K/Fe] abundance ratios for all candidates by synthesising spectra to account for the flux residuals \citep{marcs,sme,vald,ispec}. We assume that absorption due to metals is accounted for by \tc, and deviations in flux around the potassium doublet is due to an increased [K/Fe] with respect to the model. We list estimated [K/Fe] abundance ratios in Table \ref{data}, where the error includes a 0.2\,dex systematic error floor that we have applied in quadrature with the fitting errors. We applied the same method to estimate [Na/Fe] from \lamost\ spectra. We note that while enhancements in [K/Fe] or [Na/Fe] can be estimated by synthesising the flux residuals, we cannot easily estimate [Mg/Fe] depletions in the same manner because it is difficult to separate the flux contribution of [Mg/Fe] (from [$\alpha$/Fe]) from the data-driven model. For this reason, we will adopt [$\alpha$/Fe] as a conservative upper limit for [Mg/Fe].

%\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra. Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5\,dex. \todo{@andy add anything specific to Na abundance methods from LAMOST}.

@@

\subsection{Detailed chemical abundances}
\label{sec:abundances}

Upon examining [Na/Fe] as estimated from the \lamost\ spectra, two distinct populations were observed: one population making up approximately 30\% of the sample with [Na/Fe] > 0.5 -- significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011} -- and a seccond with [Na/Fe] consistent with typical galactic values. However, this behaviour is very likely due to the effect of interstellar dust. This conclusion is based on values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, which were notably higher for the stars supposedly enriched in Na than for those consistent with galactic levels. \todo{It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K. For these newly identified candidate stars, no relation between Na and K abundance is observed.}

Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. As described in Section \ref{sec:method}, we adopt [$\alpha$/Fe] as an upper limit for [Mg/Fe]. [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown. \todo{For these stars..}

%The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1\,dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data. However, for the bulk of the sample decoupling [Mg/Fe] from $[\alpha$/Fe] is impossible, and so in general  we are unable to draw firm conclusions as to whether the sample exhibits anomalously low [Mg/Fe].

[K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population. The [K/Fe] level for the candidates estimated by \lamost\ is significantly higher than the [K/Fe] abundance in NGC 2808.

Levels of [$\alpha$/Fe] fall within the lower limits for [Mg/Fe] of the Mg-normal population of both NGC 2419 and NGC 2808, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe] the exact level of Mg depletion for the candidates is unclear. The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are also consistent with the Mg-normal population in NGC 2419. However, the \lamost\ spectral data relative to \tc\ model are consistent with an under-abundance of Mg. The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] compared to NGC 2419 or NGC 2808.

Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical galactic abundances for [K/Fe], taken from \cite{kobayashi2011}. The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3. Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample has extremely high levels of [K/Fe].

The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, \todo{which is absent from measurements in the Milky Way}. It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation. \todo{make figure in python, add trend line} Due to the data-driven nature of the model, it is possible that this relation is an artefact of the process for calculating [K/Fe]; further high resolution observations are required to verify this anti-correlation.

@@

%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3\,dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}. No variation with metallicity is observed within the \lamost sample's [$\alpha$/Fe].

The implications of the estimated abundances are intriguing. The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness regarding the extreme bi-modal nature of its abundance pattern. It is worth repeating however that the sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.

The 112 star candidate pool identified of K enhanced stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels at a range of metallicities. It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.

\subsection{Impact on potential scenarios explaining the Mg-K anti-correlation}

@@

An early modelling attempt to replicate the anomalous Mg/K abundance ratios assumed hot-bottom burning in AGB and super-AGB (SAGB) stars. \cite{ventura2012} succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K. However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value. or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.

A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}. The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway. The main pathway used by \cite{iliadis2016} is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary. This constraint rules out many pollution sites, including: core and shell burning of low-mass stars, high-mass and super-massive stars, as well as regular AGB stars. Super-AGB (SAGB) stars, however, were considered as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified. The other potential candidate identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty. However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.

Our study presents a collection of stars in the disk of the galaxy at a range of metallicities showing anomalously high levels of [K/Fe]. The spread in metallicities among our candidates is important to note. It implies that the process responsible for the Mg-K abundance signature may not be tied to a certain epoch in the Milky Way's evolution. Since the stars with enhanced K and depleted magnesium apparently tend to form at all ages, across all metallicities, it is probable that the polluter star is also able to form independently of metallicity.

If we assume that the polluter star is indeed able to form at a range of metallicities, then we can attempt to constrain what sort of astrophysical scenarios may be responsible for the Mg-K anti-correlation.

One class of candidates that can be immediately eliminated as a result of such an assumption are Population III stars. A hyper-massive Population III star may have been a plausible explanation for NGC~2419 \citep{carretta2013}, particularly given it's isolation from the Milky Way ($d_{GC} \approx 90\,{\rm kpc}$) and low metallicity. However, being unable to form throughout the life of the galaxy makes it difficult -- but not impossible -- for a Population III star to be the polluter candidate responsible for the pool of stars identified in this study.

One possible polluter candidate that \textit{could} form throughout the life of the Milky Way is an SAGB-binary. As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K. Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27} Al} through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning (HBB) environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}. This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system. The SAGB-binary is hypothesised produce a [K/Fe] over-abundance in select stars within the Milky Way as follows:

The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope. It then deposits its K rich outer layers onto its smaller companion through wind-based accretion. This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not. If the companion star had sufficient mass to undergo hot-bottom burning, then Na could be produced \citep{prantzos2017}, with this material mixed throughout the envelope. Further, depending on the HBB temperature, the AGB star may also deplete Mg through Mg/Al chains. In this scenario, it is observations of the smaller binary companion star that make up our sample of 112 giants.

Although this scenario is consistent with the total spread in metallicity, it is not applicable to NGC 2419 or NGC2808; SAGB-binaries cannot account for 30\% of the stars in NGC 2419 showing depleted Mg and enhanced K abundances. Further, it would only occasionally produce a depletion in [Mg/Fe], unlike the consistent bi-modality seen in NGC 2419 and NGC 2808.

A direct test of this scenario would be to determine whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.

The spread in metallicity does not necessarily require the polluter candidate to be able to form throughout the life of the galaxy however; all that is required is that the stars observed formed in different metallicity environments. The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as indicative of a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases. This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419, shown in Figure \ref{KvsFe}. If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 112 field star sample.
